---
title: "Lab04: linreg class"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab04)
```

# What is this package?

This is a linear regression package to solve linear regression models

## linreg class
Class takes linear equation and data structure, calculates regression coefficients, fitted values, residuals, degrees of freedom, residual variance, variance of the regression coefficients, t-values and p-values.

### Methods

1. **print()**

prints formula, name of data frame and regression coeficients:

Example:
```{r include = TRUE}
print(linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris))
```
 
2. **plot()**

plots residuals vs Fitted values plot and Scale - Location plot

Example:
```{r include = TRUE}
plot(linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris))
```

3. **resid()**

returns vector of residuals

Example:
```
resid(linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris))
```

4. **pred()**

returns the predicted values

Example:
```
pred(linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris))
```
5. **coef()**

returns coefficients as a named vector

Example:
```{r include = TRUE}
coef(linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris))
```
6. **summary()**

returns the summary of linear regression model

Example:
```{r include = TRUE}
summary(linreg(Petal.Length~Sepal.Width+Sepal.Length, data=iris))
```

